Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-01 analysis/paper/paper.Rmd
update the description for terms in ERGMs

2. gwesp (geometrically weighted edgewise shared partners): a dyad-based configurations (not node-based) that counts the number of times that both nodes have a tie to a third node. It is a measure of the tendency for two actors who are tied to have x partners in common.

@@

```{r model-ergm-1}
model.ergm <- burial_network_pre ~ 
  edges + # ties, a measure of density, equal to kstar(1) for undirected networks
  density +
  gwdegree(0.5, fixed = TRUE)  +
  triangle # triad relation, a measure of clustering or cohesion, also called transitive triple in undirected network
summary(model.ergm)
```

```{r model-ergm-2}
model.2 <- burial_network_pre ~ edges + # density
  gwesp(0.2, fixed = TRUE) +  # transitivity(cohesion; triangle), a tendency for those with shared partners to become tied, or tendency of ties to cluster together
  # triad-based clustering according to dyad-based configurations instead of node-based
  # number means weight parameter alpha, which controls the rate of declining marginal returns
  # fixed = TRUE means the scale parameter lambda is fit as a curved exponential-family model
  # not much difference in a range of 0-1.5, the lower the value of the scaling parameter, the less likely the model is to be degenerate
  # ergm can estimate the parameter from the data by using fixed=FALSE
  # http://mailman13.u.washington.edu/pipermail/statnet_help/2010/000575.html
  gwdegree(0.8, fixed = TRUE)  # popularity(degree; star), the frequency distribution for nodal degrees
  # tendency of being in contact with multiple partners, measures of centralisation
  # distribution of node-based edge counts, each node counts only once
  # number means weight parameter decay
  # Morris et al. (2008)
  # The closer decay is to zero, the more gwdegree considers low degree nodes relative to high degree nodes
summary(model.2)
```

>>>>

2. gwesp (geometrically weighted edgewise shared partners): triad-based clustering based on a dyad-based configurations (not node-based) that counts the number of times that both nodes have a tie to a third node. It is a measure of the tendency for two actors who are tied to have x partners in common. In orther words, a tendency for those with shared partners to become tied, or tendency of ties to cluster together.

@@

```{r model-ergm-1}
model.ergm <- burial_network_pre ~ 
  edges + # ties, a measure of density, equal to kstar(1) for undirected networks
  density +
  gwdegree(0.5, fixed = TRUE) +
  triangle # triad relation, a measure of clustering or cohesion, also called transitive triple in undirected network, can be replaced by "gwdegree"
summary(model.ergm)
```

```{r model-ergm-2}
# check out the terms: http://mailman13.u.washington.edu/pipermail/statnet_help/2010/000575.html
# also check here Morris et al. (2008)
model.2 <- burial_network_pre ~ edges + # density
  gwesp(0.2, fixed = TRUE) +  # transitivity(cohesion; triangle)
  # number means weight parameter alpha, which controls the rate of declining marginal returns
  # fixed = TRUE means the scale parameter lambda is fit as a curved exponential-family model
  # not much difference in a range of 0-1.5, the lower the value of the scaling parameter, the less likely the model is to be degenerate
  # ergm can estimate the parameter from the data by using fixed=FALSE

  gwdegree(0.8, fixed = TRUE)  # popularity(degree; star), the frequency distribution for nodal degrees
  # tendency of being in contact with multiple partners, measures of centralisation
  # distribution of node-based edge counts, each node counts only once
  # number means weight parameter decay
  # The closer decay is to zero, the more gwdegree considers low degree nodes relative to high degree nodes
summary(model.2)
```
